---
title: "Module 4 Quiz No.1"
author: "Karl Boncodin"
date: "8/2/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

### An article in the Journal of Sound and Vibration ["Measurement of Noise-Evoked Blood Pressure by Means of Averaging Method: Relation between Blood Pressure Rise and PSL" (1991, Vol. 151(3), pp. 383-394)] described a study investigating the relationship between noise exposure and hypertension. The following data are representative of those reported in the article.

```{r, echo=FALSE}
library(readxl)
QUES1 <- read_excel("~/QUES1.xlsx")
head(QUES1, n = 20)
```

### A. Draw a scatter diagram of y (blood pressure rise in millimeters of mercury) versus x (sound pressure level in decibels). Does a simple linear regression model seem reasonable in this situation?

```{r, echo=FALSE}
X <- QUES1$X
Y <- QUES1$Y
plot(X, Y, main = "X VS. Y", xlab = "sound pressure level in decibels", ylab = "blood pressure rise in millimeters of mercury")
 abline(lm(Y~X), col="red")
```

Looking at the scatter diagram with a fitted regression line, we can see that there is a linear relationship between the values. Hence, a simple regression model in this situation seems to be reasonable.

***

### B. Fit the simple linear regression model using least squares. Find an estimate of $\sigma^2$

From the data, we get 
n = 20, $\sum{X_i}$ = 1656, $\sum{Y_i}$ = 86, $\bar{x}$ = 82.8, $\bar{y}$ = 4.3, $\sum{X_i^2}$ = 140,176, $\sum{Y_i^2}$ = 49, $\sum{X_iY_i}$ = 7654

Using these data, we first get $S_{xx}$ using the formula:
$$
  S_{xx} ~ = ~ \sum{X_i^2}~-~\frac{(\sum{X_i})^2}{n}
$$
So:
$$
  S_{xx} ~ = ~ 140,176~-~\frac{(1656)^2}{20}~= ~ 3,059.2
$$

We then get $S_{xy}$ using the formula:
$$
  S_{xy}~=~\sum{X_iY_i}~-~\frac{(\sum{Y_i})(\sum{X_i})}{n}
$$

So,
$$
  S_{xy}~=~7,654~-~\frac{(86)(1656)}{20}~=~533.2
$$

Using the values obtained for $S_{xx}$ and $S_{xy}$ we can get the coefficient $\hat{\beta_1}$ with
$$
  \hat{\beta_1} ~=~\frac{S_{xy}}{S_{xx}}~=\frac{533.2}{3059.2}~=~0.17429
$$
So $\hat{\beta_1}$ = 0.17429

Now with $\hat{\beta_1}$, we can solve for the intercept $\hat{\beta_0}$ with the values of $\bar{y}$ and $\bar{x}$:
$$
  \hat{\beta_0}~=~\bar{y}~-~\hat{\beta_1}\bar{x}~=~4.3 ~-~(0.17429)(82.8)~=~-10.13121
$$
So $\hat{\beta_0}$ = -10.13121


Using the values of $\hat{\beta_0}$ and $\hat{\beta_1}$, Our simple regression model is:
$$
  \hat{y}~= \hat{\beta_0}~+~\hat{\beta_1}x ~:~ \hat{y}~=-10.13121~+~0.17429x
$$
So our regression model is:

***$\hat{y}$ = -10.13121 + 0.17429x***


Estimating $\sigma^2$:
$$
  \sigma^2~=~\frac{SS_E}{n-2}~where~SS_E~=~SS_T~-~\hat{\beta_1}S_{xy}
$$
$$
SS_T~=~\sum{Y_i^2~-~n\bar{y}^2}~=~494~-(20)(4.3)^2~=~124.2
$$
$$
SS_E~=~124.2~-~(0.17429)(533.2)~=~31.268572
$$



Getting the estimated $\sigma^2$:
$$
\sigma^2~=~\frac{SS_E}{n-2}~=~\frac{31.268572}{20-2}~=~1.73714
$$

***Our estimated $\sigma^2$ is 1.73714***

***


### C.Find the predicted mean rise in blood pressure level associated with a sound pressure level of 85 decibels.

Letting x = 85 and using the simple regression model
$$
  \hat{y}~=-10.13121~+~0.17429x
$$
Substituting the value of x we get:
$$
  \hat{y}~=-10.13121~+~0.17429(85)~=~4.68255
$$

So, The predicted mean rise in blood pressure level associated with a sound pressure level of 85 decibels is ***4.68255***